\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-08-13 manuscript/main.tex
new file:   archived manuscript/main.tex 	new file:   archived manuscript/our-cites.bib 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@

While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market. Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service. Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy. Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes. Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts. Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset. Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.

@@

Our research has several implications. Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies. This shift underscores the need for firms to enhance their digital strategies to remain competitive. Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering. For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform. Thirdly, this study demonstrates that, under the platform's consolidation effect, offline stores can enhance revenue and improve transaction efficiency. These findings can be extended to other similar fields, as discussed by \citep{10.1257/jep.28.2.3}. Lastly, this study also confirms that local network effect can not preclude other competitors from entering the market but the network effect can help the company to coexist with other competitors, and improve the overall market efficiency, consistent with the work by \citep{gilbukh_goldsmith-pinkham_2019}.

@@

>>>>

% bergemann_data_2024

@@

While the co-listing strategy—listing properties with multiple brokerages—has been suggested as beneficial in some markets, such as under a multiple-listing service \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, it is suboptimal within China's real estate context for several reasons. First, exclusive contracts between sellers and agents typically preclude co-listing, thereby limiting its feasibility. Second, although sellers can list with multiple brokerages, smaller agencies often lack a sufficient client base, reducing their effectiveness. Third, engaging multiple brokers can dilute agent incentives due to perceived competition, leading to less proactive efforts. Finally, while agency service cost differences exist, these costs are relatively minor compared to the property's value and are more closely related to the financial risks involved. Consequently, risk-averse sellers tend to prefer agencies offering a guaranteed service level. Moreover, \citet{bergemann_data_2024} finds that when platforms possess significant bargaining power, co-listing with multiple agents is no more efficient than listing with a single agent.

@@

Our research has several implications. Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies. This shift underscores the need for firms to enhance their digital strategies to remain competitive. Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering. For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform. Thirdly, this study demonstrates that, under the platform's consolidation effect, offline stores can enhance revenue and improve transaction efficiency. These findings can be extended to other similar fields, as discussed by \citep{10.1257/jep.28.2.3}. Fourthly, this study also confirms that local network effect can not preclude other competitors from entering the market but the network effect can help the company to coexist with other competitors, and improve the overall market efficiency, consistent with the work by \citep{gilbukh_goldsmith-pinkham_2019}. Lastly, our paper use empirical data to shows the broad implication of the research \citep{bergemann_data_2024}, where the platform can benefits from increased bargaining power vis-\'a-vis sellers by exploiting its information advantage.

@@

\bibitem[Bergemann and Bonatti(2024)]{bergemann_data_2024}
Bergemann D, Bonatti A (2024) Data, Competition, and Digital Platforms. American Economic Review 114(8):2553-2595.
